Understanding meta-analysis through data simulation with applications to power analysis

### 2023-09-06 documents/paper/paper.tex
updating

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{meta-analysis, monte carlo simulations, power analysis\newline\indent Word count: 7782}
\usepackage{csquotes}
\usepackage{setspace}
\captionsetup[figure]{font={stretch=1,footnotesize}}
\usepackage{float}
\usepackage{orcidlink}
\newcommand{\rev}[1]{\textcolor{red}{#1}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Understanding meta-analysis through data simulation with applications to power analysis},
  pdfauthor={Filippo Gambarota 1 \& Gianmarco Altoè 1},
  pdflang={en-EN},
  pdfkeywords={meta-analysis, monte carlo simulations, power analysis},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

The aim of the tutorial is not providing a complete theoretical introduction to meta-analysis but presenting the core topics using a simulation-based approach. Readers expert in conducting meta-analyses could benefit more from the proposed approach in terms of simulation setup and coding strategies. Readers without experience in meta-analysis could benefit both from the theoretical introduction and the simulation approach. However, for a better and extensive overview of meta-analysis topics the reader could refer to Harrer, Cuijpers, and Ebert (2019), and Borenstein et al. (2009).

>>>>

\usepackage{xpatch}
\makeatletter
\xapptocmd\appendix
  {\xapptocmd\section
    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
    {}{\InnerPatchFailed}%
  }
{}{\PatchFailed}
\keywords{meta-analysis, monte carlo simulations, power analysis\newline\indent Word count: 7866}
\usepackage{csquotes}
\usepackage{setspace}
\captionsetup[figure]{font={stretch=1,footnotesize}}
\usepackage{float}
\usepackage{orcidlink}
\newcommand{\rev}[1]{\textcolor{red}{#1}}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Understanding meta-analysis through data simulation with applications to power analysis},
  pdfauthor={Filippo Gambarota 1 \& Gianmarco Altoè 1},
  pdflang={en-EN},
  pdfkeywords={meta-analysis, monte carlo simulations, power analysis},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

The aim of the tutorial is not providing a complete theoretical introduction to meta-analysis but presenting the core topics using a simulation-based approach. Readers expert in conducting meta-analyses could benefit more from the proposed approach in terms of simulation setup and coding strategies. Readers without experience in meta-analysis could benefit both from the theoretical introduction and the simulation approach. However, for a better and extensive overview of meta-analysis topics the reader could refer to meta-analysis textbooks (Borenstein et al., 2009; e.g., Harrer, Cuijpers, \& Ebert, 2019).
